---
title: "Exploring Activity Monitor Data"
output: 
  html_document:
    keep_md: true
---



## Loading and preprocessing the data

If you don't have the data, you can find it [here](https://github.com/mattayes/RepData_PeerAssessment1/blob/master/activity.zip?raw=true).

Let's start by reading our data in. I'll be using the dplyr package later, so I'll add a `tbl_df` wrapper now.

```{r read, echo = FALSE}
library(dplyr)
activity <- tbl_df(read.csv("./activity.csv",
                            stringsAsFactors = FALSE,
                            colClasses = c("integer", "Date", "integer")
                            )
                   )
```

Let's take a quick peek at our data to see what we're working with.

```{r peek}
activity
```

We can see that there's three variables:

- **steps**: number of steps taken in a five-minute interval (missing values are coded as `NA`)

- **date**: the date on which the measurement was taken

- **interval**: identifier for the five-minute interval in which the measurement was taken

I think it would look better if interval were in HHMM format. It will also plot better if we convert it to a factor. Let's make it happen.

``` {r formatC}
activity <- activity %>%
    mutate(interval = formatC(interval, width = 4, format = "d", flag = "0"),
           interval = factor(interval)
           )
activity
```

Finally, because aesthetics REALLY matters to me, I'm going to put steps as the last variable.

```{r format}
activity <- activity %>%
    select(date, interval, steps)
activity
```

With that out of the way, let's do some analysis!

## What is mean total number of steps taken per day?



## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
